\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-10 paper/ms.tex
Writing about proposals

The \code{perturb} member function is:

When implementing a model class, it is imperative that the
\code{from\_prior(DNest4::RNG\&)} and \code{perturb(DNest4::RNG\&)}
member functions be consistent with each other.

>>>>

After generating the parameters from the prior, another member function
\code{calculate\_mu()} is called, which computes the model prediction
$mx_i + b$ for each data point.

The \code{perturb} member function for the straight line model is:
\begin{CodeChunk}
\begin{CodeInput}
double StraightLine::perturb(DNest4::RNG& rng)
{
	double log_H = 0.0;

	// Proposals explore the prior
	// For normal priors I usually use the hastings factor to do it
	int which = rng.rand_int(3);
	if(which == 0)
	{
		log_H -= -0.5*pow(m/1E3, 2);
		m += 1E3*rng.randh();
		log_H += -0.5*pow(m/1E3, 2);
	}
	else if(which == 1)
	{
		log_H -= -0.5*pow(b/1E3, 2);
		b += 1E3*rng.randh();
		log_H += -0.5*pow(b/1E3, 2);
	}
	else
	{
		// Usual log-uniform prior trick
		sigma = log(sigma);
		sigma += 20.0*rng.randh();
		DNest4::wrap(sigma, -10.0, 10.0);
		sigma = exp(sigma);
	}

	// Calculate mu again if m or b changed
	if(which == 0 || which == 1)
		calculate_mu();

	return log_H;
}
\end{CodeInput}
\end{CodeChunk}

This first chooses a random integer from $[0, 3)$ using the
\code{rand\_int(int)} member function of the \code{DNest4::RNG} class.

When implementing a model class, it is imperative that the
\code{from\_prior(DNest4::RNG\&)} and \code{perturb(DNest4::RNG\&)}
member functions be consistent with each other. One technique
for verifying this is to sample the prior for a long time
(by setting the maximum number of levels to 1) and inspect
{\tt sample.txt} to ensure that each parameter is exploring
the correct distribution.
